Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2023-12-06 demystify.tex
updates

\begin{commentbox}
    [DK:] Here are a few items you may consider addressing: putting international students in touch with other students from their countries, assuring them that they would be picked up from airports upon their arrival and that their initial stay will be taken care of. Most universities have other resources for these, but it is worth mentioning that they would be taken care of upon arrival and can get help during the transition phase. Learning to cook was a big deal when I arrived over 50 years ago-August 1973. But things have changed as one can find many ethnic food places, a big contrast from 1973, when there were two Indian restaurants in Greater Boston area.
\end{commentbox}

>>>>

% \begin{commentbox}
%     [DK:] Here are a few items you may consider addressing: putting international students in touch with other students from their countries, assuring them that they would be picked up from airports upon their arrival and that their initial stay will be taken care of. Most universities have other resources for these, but it is worth mentioning that they would be taken care of upon arrival and can get help during the transition phase. Learning to cook was a big deal when I arrived over 50 years ago-August 1973. But things have changed as one can find many ethnic food places, a big contrast from 1973, when there were two Indian restaurants in Greater Boston area.
% \end{commentbox}
